---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rpackage

<!-- badges: start -->
<!-- badges: end -->

This R package was created to experiment with the R creation process and simplify the import of DNA sequenes, translation of DNA sequences and reversal of DNA sequences.

## Installation

You can install the development version of Rpackage from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ADC-405-S26/DNAtranslate")
```

## Example

This is a basic example which shows you how import a DNA sequence, reverse it, and then translate it into proteins.

```{r readSequences}
library(DNAtranslate)
# import a .txt file formatted as followed 
# >Sequence Name
# ATGCATGCATGCATGCATGCATGC
# ATGCATGCATGC...
sequencesDF <- readSequences("data-raw/exampleSequences.txt")
head(sequencesDF)

```

```{r reverseSequence}
library(DNAtranslate)
# take that previously created DF and flip a specified sequence
reverse <- reverseSequence(exampleSequences, "HisD TA1538 Mutant Genotype")
head(reverse)
# now the sequence with the name "HisD TA1538 Mutant Genotype" is flipped
```

```{r translate DNA}
library(DNAtranslate)
# add a new column to the sequence DF with the protein sequence that corresponds with the DNA sequence
proteinSequence <- translateDNA(exampleSequences, offset = 0)
head(proteinSequence)
```
